Holomorphic field theories and higher algebra

### 2024-09-20 draft.tex
must have done some stuff

\epigraph{\itshape The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}

>>>>

\epigraph{The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}
